\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payoff Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-19 latex/article.tex
without numerical implementation

where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
the position weights, \( \gamma \) is the regularization parameter, and 
\( S_{\min}, S_{\max} \) define the approximation domain. The L2 norm promotes 
smoother weight distributions, providing stability to the solution.

Discretizing the integral and using matrix notation, we obtain:

@@

    \item \textbf{Weighted Error Function:} Incorporating target function magnitude 
    into the error term:
    \begin{equation}
        L(\boldsymbol{\theta}) = 
            \int_{S_{\min}}^{S_{\max}} 
                V(S) \Big| V(S) - \hat{V}(S;\boldsymbol{\theta}) \Big| dS + 
            \gamma \|\boldsymbol{\theta}\|_p^p
    \end{equation}
    This formulation provides error weighting proportional to the target payoff magnitude, 
    offering economic interpretation well-aligned with trading objectives. Furthermore, it 
    naturally enhances focus on regions with significant payoff values, making it particularly 
    suitable for practical applications.
\end{enumerate}

However, these generalizations lose the analytical tractability of the L2 case, 
requiring numerical optimization methods for solution.

\subsection{Numerical Implementation}
The implementation leverages the analytical solution derived in the Mathematical Framework 
section for L2-regularized problems. For L1 regularization and alternative loss functions, 
numerical optimization methods are employed.

Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization 
approaches in approximating a complex payoff profile. The target function combines 
different types of functions, presenting a challenging test case. Both 
methods achieve good approximation quality, with L2 regularization providing slightly 
smoother results and L1 regularization favoring a sparser representation with fewer 
non-zero option weights.

@@

Figure~\ref{fig:weighted} illustrates the performance of the weighted error method, 
which places greater emphasis on accurately approximating regions with larger payoff 
values. This approach is particularly useful when the economic significance of errors 
varies with the magnitude of the target payoff, providing a more practical solution 
for trading applications.

@@

This comprehensive comparison suggests that for practical applications, the weighted error 
method should be preferred despite its requirement for numerical optimization. The improved 
accuracy (approximately 30\% reduction in MAE compared to L2) and consistent performance 
across different regularization parameters justify the additional computational cost. 
Furthermore, the weighted method's focus on economically significant regions makes it 
particularly well-suited for real-world trading applications.

@@

\begin{equation}
\boldsymbol{\theta}^* = 
    \argmax_{\boldsymbol{\theta}} 
        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right] - 
\end{equation}

>>>>

where \( \boldsymbol{\theta} = (\lambda, \{\alpha_i\}, \{\beta_j\}) \) represents
the position weights, \( \gamma \) is the regularization parameter, and 
\( S_{\min}, S_{\max} \) define the approximation domain.

The L2 norm promotes smoother weight distributions, providing stability to the solution.
Discretizing the integral and using matrix notation, we obtain:

@@

    \item \textbf{Weighted Error Function:} Incorporating target function magnitude 
    into the error term:
    \begin{equation}
        L(\boldsymbol{\theta}) = 
            \int_{S_{\min}}^{S_{\max}} 
                V(S) \Big| V(S) - \hat{V}(S;\boldsymbol{\theta}) \Big| dS + 
            \gamma \|\boldsymbol{\theta}\|_p^p
    \end{equation}
\end{enumerate}

@@

The weighted error formulation provides error weighting proportional to the target payoff magnitude, 
offering economic interpretation well-aligned with trading objectives. Furthermore, it 
naturally enhances focus on regions with significant payoff values, making it particularly 
suitable for practical applications.

@@

This comprehensive comparison suggests that for practical applications, the weighted error 
method should be preferred despite its requirement for numerical optimization. The improved 
accuracy (approximately 30\% reduction in MAE compared to L2) and consistent performance 
across different regularization parameters justify the additional computational cost.

@@

\begin{equation}
\boldsymbol{\theta}^* = 
    \argmax_{\boldsymbol{\theta}} 
        \mathbb{E}\left[\hat{V}(S_T;\boldsymbol{\theta})\right]
\end{equation}
